Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-05-15 writing/embedded_meta_learning.tex
Further Tweaks

However, the system is not limited to simply mapping inputs to outputs. The key advantage of our architecture is that it allows transforming anything that is embedded in $Z$ using the same system. For example, suppose we have some task embedding $z_{old} \in Z$, and a meta-mapping embedding $z_{\text{meta}} \in Z$, e.g. from $z_{\text{meta}} = \mathcal{M}\left( \left\{\left((z_{source,0},z_{target,0}\right) \right\}\right)$. Then we can generate a new task embedding $\hat{z}_{new} \in Z$ as:  

@@

\paragraph{Conclusions:} In this paper, we've highlighted a new type of flexibility in the form of \emph{meta-mappings}, that is, mappings between tasks. We've suggested that achieving this type of flexibility is difficult in most deep learning architectures, because they separate computation from the knowledge of what is being computed. We've proposed that explicitly representing the tasks by embeddings, and deriving the computation from these embeddings, provides a solution to this problem. To this end, we've proposed a meta-learning system which embeds tasks and data into a shared latent space, and then meta-learns to make mappings over this space. The requisite meta-task sample complexity is small; we showed generalization to unseen meta-mappings after training on only 20 meta-mappings.\par

>>>>

However, the system is not limited to simply mapping inputs to outputs. The key advantage of our architecture is that it allows transforming anything that is embedded in $Z$ using the same system. For example, suppose we have some task embedding $z_{old} \in Z$, and a meta-mapping embedding $z_{\text{meta}} \in Z$, e.g. from $z_{\text{meta}} = \mathcal{M}\left( \left\{\left((z_{source,0},z_{target,0}, ...\right) \right\}\right)$. Then we can generate a new task embedding $\hat{z}_{new} \in Z$ as:  

@@

\paragraph{Conclusions:} In this paper, we've highlighted a new type of flexibility in the form of \emph{meta-mappings}, that is, mappings between tasks. We've suggested that achieving this type of flexibility is difficult in most deep learning architectures, because they separate computation from the knowledge of what is being computed. To address this, we've proposed explicitly representing the tasks by embeddings, and deriving the computation from these embeddings via a HyperNetwork. This allows transformations over task embeddings to transform the system's behavior. To this end, we've proposed a meta-learning system which embeds tasks and data into a shared latent space, and then meta-learns to make mappings over this space. The requisite meta-task sample complexity is small; we showed generalization to unseen meta-mappings after training on only 20 meta-mappings.\par
